scRNAseq benchmark in want of a title

### 2019-05-27 bmc_article.tex
Updates from Overleaf

The impact of the dimensionality reduction method was far greater than that of normalization or feature selection (e.g. Supplementary Figure 19). Although the first components identified by GLM-PCA tended to have a higher proportion of their variance explained by real subpopulations and increase the average silhouette width of already well-defined subpopulations, overall Seurat's PCA procedure proved superior on all metrics (Figure 5 and Supplementary Figures 19-21). 
In particular, weighing the components had a strong positive impact on silhouette widths and resulting ARI.

@@

\subsection*{Filter sets}
The \textit{default} set of filters excludes cells that are outliers according to at least two of the following thresholds: log10_total_counts $>$2.5 MADs or $<$5 MADs, log10_total_features $>$2.5 MADs or $<$5 MADs, pct_counts_in_top_20_features $>$ or $<$ 5 MADs, featcount_dist (distance to expected ratio of log10 counts and features) $>$ or $<$ 5 MADs, pct_counts_Mt $>$ 2.5 MADs and $>$ 0.08.

@@

The \textit{lenient} set of filters excludes cells that are outliers on at least two distributions by at least 5 MADs, except for pct_counts_Mt where the threshold is $>$ 3 MADs and $>$ 0.08.

>>>>

The impact of the dimensionality reduction method was far greater than that of normalization or feature selection (e.g. Supplementary Figure 19). Although the first components identified by GLM-PCA tended to have a higher proportion of their variance explained by real subpopulations and increase the average silhouette width of already well-defined subpopulations, overall Seurat's PCA procedure proved superior on all metrics (Figure \ref{fig:figure5} and Supplementary Figures 19-21). 
In particular, weighing the components had a strong positive impact on silhouette widths and resulting ARI.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{{main_figures/figure5_dr_files/figure-html/unnamed-chunk-2-1.png}}
    \caption{Evaluation of the dimensionality reduction strategies.}
    \label{fig:figure5}
\end{figure}

@@

\subsection*{Filter sets}
The \textit{default} set of filters excludes cells that are outliers according to at least two of the following thresholds: log10\_total\_counts $>$2.5 MADs or $<$5 MADs, log10\_total\_features $>$2.5 MADs or $<$5 MADs, pct\_counts\_in\_top\_20\_features $>$ or $<$ 5 MADs, featcount\_dist (distance to expected ratio of log10 counts and features) $>$ or $<$ 5 MADs, pct\_counts\_Mt $>$ 2.5 MADs and $>$ 0.08.

@@

The \textit{lenient} set of filters excludes cells that are outliers on at least two distributions by at least 5 MADs, except for pct\_counts\_Mt where the threshold is $>$ 3 MADs and $>$ 0.08.

For cluster-wise filters, clusters were first identified with \textit{scran::quickCluster} and the filters were then applied separately for each cluster.
